An Ant Cuticle Texture Classification Algorithm for Ecological Anaylsis

### 2021-09-03 paper/paper.tex
add cc attribution
add experiment 1 results

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\textwidth]{assets/images/segmented_1.png}
  \caption{Hand segmented ant head image to separate head cuticle from other
    sections of the image.
    \href{https://www.antweb.org/bigPicture.do?name=casent0217419&shot=h&number=1}{CASENT0217419}
    by \href{https://www.antweb.org/artist.do?id=92}{Estella Ortega}, from
    \href{https://www.antweb.org}{AntWeb}}
  \label{fig:segmented_1}
\end{figure}

@@

In the first experiment, we investigate the ability of a basic CNN to classify
cuticle texture into the two main categories: \textit{rough} and
\textit{smooth}. The goal of this experiment is to determine if more intricate
data preprocessing is necessary to classify the texture of the ant. The dataset
used is shown in Table \ref{table:classdist_rs_full}, and the results are shown
in (TODO).

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\textwidth]{assets/images/segmented_1.png}
  \caption{Hand segmented ant head image to separate head cuticle from other
    sections of the image.
    \href{https://www.antweb.org/bigPicture.do?name=casent0217419&shot=h&number=1}{CASENT0217419}
    by \href{https://www.antweb.org/artist.do?id=92}{Estella Ortega}, from
    \href{https://www.antweb.org}{AntWeb}, is licensed under
    \href{https://creativecommons.org/licenses/by/4.0/}{CC BY 4.0}}
  \label{fig:segmented_1}
\end{figure}

@@

In the first experiment, we investigate the ability of a basic CNN to classify
cuticle texture into the two main categories: \textit{rough} and
\textit{smooth}. The goal of this experiment is to determine if more intricate
data preprocessing is necessary to classify the texture of the ant. Images were
resized to different sizes for CNN input and different samples per class were
also tested.The dataset used is shown in Table \ref{table:classdist_rs_full},
and the results are shown in Table \ref{table:exp1_full}.

\begin{table}[h]
  \centering
  \caption{Binary Classification of Full Size Images}
  \label{table:exp1_full}
  \include{tables/experiment_1.tex}
\end{table}
